New Biomass Pools Workflow

### 2023-10-04 NewBiomassPoolsWorkflow.Rmd
fix sedlayer bug but calc still off for LG_PHY

@@

    pooln <- pooln |>
      dplyr::mutate(atoutput = dplyr::case_when(pooltype == "nonbenth" ~ vol * atoutput * bio_conv,
                                                pooltype == "benthos" ~ 
                                                  ifelse(layer==7, area * atoutput * bio_conv, 0)))

@@

```{r, warning=FALSE}

@@

@@

@@

>>>>

    sedlayer <- max(vol$layer)

@@

    pooln <- pooln |>
      dplyr::mutate(atoutput = dplyr::case_when(pooltype == "nonbenth" ~ vol * atoutput * bio_conv,
                                                pooltype == "benthos" ~ 
                                                  ifelse(layer==sedlayer, area * atoutput * bio_conv, 0)))

@@

```{r, warning=FALSE, fig.width=10}

@@

### Try NEUS?

```{r}
dir <- here("atlantisoutput/NEUSv2.1.0")
file_nc <- "neus_output.nc"

For NEUS Atlantis, these are the biomass pools:

fgs <- atlantisom::load_fgs(here("atlantisoutput/NEUSv2.1.0"), "neus_groups.csv")

pools <- fgs %>%
  dplyr::filter(NumCohorts==1) %>%
  dplyr::select(Code, Name, LongName, NumCohorts, GroupType)

```
NEUS has some Cover types as well as N outputs.

select_groups <- pools$Name
nc_out <- file_nc
bps <- load_bps(dir = dir, fgs = "neus_groups.csv", file_init = "neus_init.nc")
  # Get the boundary boxes
  allboxes <- load_box(dir = dir, file_bgm = "neus_tmerc_RM2.bgm")
  boxes <- get_boundary(allboxes)

unique(testNpools$species)
```
```{r}

# we need area for the benthic inverts instead of volume
# THANK YOU JOE for this tip
area <- load_boxarea(dir = dir,
                     file_bgm = "neus_tmerc_RM2.bgm")

biolprm <- load_biolprm(dir = dir, file_biolprm = "at_biology.prm")

txtbiopools <- atlantisom::load_bioind(dir, "neus_outputBiomIndx.txt", fgs) %>%
  dplyr::mutate(time = time/73) %>%
  dplyr::filter(species %in% unique(aggbiopools$species)) %>%
  dplyr::select(species, time, atoutput)

```
mismatch

ggplot(mismatch, aes(x=time, y=mismatch)) +
  geom_line() +
  theme_bw() +
  facet_wrap(~species, scales = 'free_y')
```
This is mismatch coded as 0 if less than 1% of txt output, 1 if more.

```{r, warning=FALSE, fig.width=10}

Learned that we should not hardcode the sediment layer! Added a sedlayer variable to the function.

BUT. Diatoms are still off so this calculation may not be working for that category.

```{r}
ggplot(txtbiopools |> filter(species %in% c("Diatom", "DinoFlag")), 
       aes(x=time, y=atoutput)) +
  geom_line() +
  geom_point(data = aggbiopools |> filter(species %in% c("Diatom", "DinoFlag")), 
             aes(x = time, y = totpool), colour = "blue") +
  theme_bw() +
  facet_wrap(~species, scales = "free_y")

@@

With an if statement?

@@

Only need species and index here, comps don't apply.
